Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
three last typos

The majority of specifications generated were relatively simple but we
found significant numbers of more complex shapes. We grouped common
patterns in to categories:

@@

The single- and multi-action classes represent more complex stencils
with a real possibility for programmer error. As an extreme example, the Unified
Model has an implementation of the Smagorinsky subgrid-scale model for
calculating turbulence on which our inference yields 39 specs from 340
lines of code. This is an large reduction given
the complexity of the algorithm.  We show one example
in~\Cref{fig:smagorinsky} which specifies the access pattern to
a 3-dimensional array (which we have renamed to 
\texttt{x}) arising from a kernel of 93 lines of code involving 142
array subscripts. The specification was the most complex
seen in our corpus, yet it still represents a significant abstraction
of the spatial behaviour given size and complexity of the kernel it describes.

@@

Our restrictive definition of stencils means we do note generate
specifications for a large number of iterated array accesses in the
corpus, \eg{} that incorporate reductions. For
future work, we will look at expanding the flexibility of 
our analysis to include these examples.

>>>>

The majority of specifications generated were relatively simple but we
found significant numbers of more complex shapes. We grouped common
patterns into categories:

@@

The single- and multi-action classes represent more complex stencils
with a real possibility for programmer error. As an extreme example, the Unified
Model has an implementation of the Smagorinsky subgrid-scale model for
calculating turbulence on which our inference yields 39 specs from 340
lines of code. This is a large reduction given
the complexity of the algorithm.  We show one example
in~\Cref{fig:smagorinsky} which specifies the access pattern to
a 3-dimensional array (which we have renamed to 
\texttt{x}) arising from a kernel of 93 lines of code involving 142
array subscripts. The specification was the most complex
seen in our corpus, yet it still represents a significant abstraction
of the spatial behaviour given size and complexity of the kernel it describes.

@@

Our restrictive definition of stencils means we do not generate
specifications for a large number of iterated array accesses in the
corpus, \eg{} that incorporate reductions. For
future work, we will look at expanding the flexibility of 
our analysis to include these examples.
